Spatial Reasoning and Statistical Graphics

### 2014-10-17 Paper/Draft1/TestingVisualAptitude.Rnw
Fix  label repetition

>>>>

\caption{Comparison of scores from Iowa State students and scores reported in \citet{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available.\label{tab:scorecomparison2}}
\end{table}
\end{savenotes}
